Copykat CNV results exploration for `r params$sample_id`

### 2024-11-12 analyses/cell-type-wilms-tumor-06/notebook_template/05_copykat_exploration.Rmd

---
title: "Copykat CNV results exploration for `r params$sample_id`"
author: "Maud PLASCHKA"
date: "`r Sys.Date()`"
params:
  sample_id: "SCPCS000194"
  seed: 12345
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE,
                      message=FALSE,
                      warnings=FALSE
)

```

@@

```{r}

subdiagnosis <- readr::read_tsv(
  file.path("..", "..", "..", "data", "current", "SCPCP000006", "single_cell_metadata.tsv"),
  show_col_types = FALSE
) |>
  dplyr::filter(scpca_sample_id == params$sample_id) |>
  dplyr::pull(subdiagnosis)

```

@@

```{r}

result_dir <- file.path(module_base, "results", params$sample_id)
predictions_paths <- list()
full_ck_result_paths <- list()
for(ref_value in c("ref", "noref")){
  for(distance_value in c("euclidean", "spearman")){
    predictions_file <- glue::glue("05_copykat_", {params$sample_id}, "_",ref_value,"_distance-", distance_value, "_copykat_prediction.txt")
    full_ck_result_file <- glue::glue("05_copykat_", {params$sample_id}, "_",ref_value,"_distance-", distance_value, "_copykat_CNA_results.txt")

@@

### Load the pre-processed `Seurat` object
```{r load, message=FALSE, warning=FALSE}
# open the processed rds object
srat <- readRDS(file.path(result_dir, paste0("02b-fetal_kidney_label-transfer_", params$sample_id,".Rds")))
DefaultAssay(srat) <- "SCT"
```

@@

![](`r file.path(result_dir, "05_copyKAT", "noref", "euclidean", glue::glue("05_copykat_", params$sample_id, "_noref_distance-euclidean_copykat_heatmap.png"))`)

@@

![](`r file.path(result_dir, "05_copyKAT", "noref", "spearman", glue::glue("05_copykat_", params$sample_id, "_noref_distance-spearman_copykat_heatmap.png"))`)

@@

![](`r file.path(result_dir, "05_copyKAT", "ref", "euclidean", glue::glue("05_copykat_", params$sample_id, "_ref_distance-euclidean_copykat_heatmap.png"))`)

@@

![](`r file.path(result_dir, "05_copyKAT", "ref", "spearman", glue::glue("05_copykat_", params$sample_id, "_ref_distance-spearman_copykat_heatmap.png"))`)

@@

# get umap coordinate
umap_df <- srat[["umap"]]@cell.embeddings |>
  as.data.frame() |>
  rownames_to_column('barcodes')

cnv_df <- umap_df |>
  dplyr::left_join(ck_results_df, by = c("barcodes" = "cell.names"))

```

@@

# join with cnv info
cnv_df <- cnv_df |>
   dplyr::left_join(full_cnv_df, by = c("barcodes", "reference_used")) |>
   dplyr::filter(!is.na(chrom))

```

>>>>

---
title: "Copykat CNV results exploration for `r params$sample_id`"
author: "Maud PLASCHKA"
date: "`r Sys.Date()`"
params:
  sample_id: "SCPCS000179"
  seed: 12345
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warnings = FALSE
)
```

@@

```{r}
subdiagnosis <- readr::read_tsv(
  file.path("..", "..", "..", "data", "current", "SCPCP000006", "single_cell_metadata.tsv"),
  show_col_types = FALSE
) |>
  dplyr::filter(scpca_sample_id == params$sample_id) |>
  dplyr::pull(subdiagnosis)
```

@@

```{r}
result_dir <- file.path(module_base, "results", params$sample_id)
predictions_paths <- list()
full_ck_result_paths <- list()
for (ref_value in c("ref", "noref")) {
  for (distance_value in c("euclidean", "spearman")) {
    predictions_file <- glue::glue(
      "05_copykat_",
      {
        params$sample_id
      },
      "_",
      ref_value,
      "_distance-",
      distance_value,
      "_copykat_prediction.txt"
    )
    full_ck_result_file <- glue::glue(
      "05_copykat_",
      {
        params$sample_id
      },
      "_",
      ref_value,
      "_distance-",
      distance_value,
      "_copykat_CNA_results.txt"
    )

@@

### Load the pre-processed `Seurat` object
```{r load, message=FALSE, warning=FALSE}
# open the processed rds object
srat <- readRDS(file.path(result_dir, paste0("02b-fetal_kidney_label-transfer_", params$sample_id, ".Rds")))
DefaultAssay(srat) <- "SCT"
```

@@

![](`r file.path(result_dir, "05_copyKAT", "noref", "euclidean", glue::glue("05_copykat_", params$sample_id, "_noref_distance-euclidean_copykat_heatmap.jpg"))`)

@@

![](`r file.path(result_dir, "05_copyKAT", "noref", "spearman", glue::glue("05_copykat_", params$sample_id, "_noref_distance-spearman_copykat_heatmap.jpg"))`)

@@

![](`r file.path(result_dir, "05_copyKAT", "ref", "euclidean", glue::glue("05_copykat_", params$sample_id, "_ref_distance-euclidean_copykat_heatmap.jpg"))`)

@@

![](`r file.path(result_dir, "05_copyKAT", "ref", "spearman", glue::glue("05_copykat_", params$sample_id, "_ref_distance-spearman_copykat_heatmap.jpg"))`)

@@

# get umap coordinate
umap_df <- srat[["umap"]]@cell.embeddings |>
  as.data.frame() |>
  rownames_to_column("barcodes")

cnv_df <- umap_df |>
  dplyr::left_join(ck_results_df, by = c("barcodes" = "cell.names"))
```

@@

# join with cnv info
cnv_df <- cnv_df |>
  dplyr::left_join(full_cnv_df, by = c("barcodes", "reference_used")) |>
  dplyr::filter(!is.na(chrom))
```
